---
title: ""
output:
  html_document:
    theme: null
    highlight: null
    self_contained: true
    css: !expr NULL
params:
  data_path: "/tmp/sleeper_data.json"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE,
                      fig.width=10, fig.height=6,
                      out.width="100%", dpi=150)

library(jsonlite); library(dplyr); library(tidyr); library(ggplot2)
library(ggrepel);  library(scales); library(stringr); library(tibble)
library(purrr);    library(forcats); library(knitr)

`%||%` <- function(a, b) if (is.null(a)) b else a

# ---- Palette ----
bg_dark  <- "#0A1628"; bg_mid <- "#0D1F3C"; bg_card <- "#112244"
col_blue <- "#4A9EDB"; col_white <- "#FFFFFF"; col_dim <- "#8AAAC8"
col_green <- "#5CBF8A"; col_red <- "#E05C5C"; col_gold <- "#F0C040"

tw <- function(base_size=11) {
  theme_minimal(base_size=base_size) %+replace% theme(
    plot.background  = element_rect(fill=bg_dark,  color=NA),
    panel.background = element_rect(fill=bg_mid,   color=NA),
    panel.grid.major = element_line(color="#1A2E50", linewidth=0.4),
    panel.grid.minor = element_blank(),
    axis.text        = element_text(color=col_dim),
    axis.title       = element_text(color=col_white),
    plot.title       = element_text(color=col_white, face="bold", size=base_size+2),
    plot.subtitle    = element_text(color=col_dim, size=base_size-1),
    plot.caption     = element_text(color=col_dim, size=base_size-3),
    legend.background= element_rect(fill=bg_mid, color=NA),
    legend.text      = element_text(color=col_dim),
    legend.title     = element_text(color=col_white),
    strip.background = element_rect(fill=bg_card, color=NA),
    strip.text       = element_text(color=col_white, face="bold")
  )
}

# ---- NFL team colors ----
nfl1 <- c(ARI="#97233F",ATL="#A71930",BAL="#241773",BUF="#00338D",CAR="#0085CA",
  CHI="#0B162A",CIN="#FB4F14",CLE="#311D00",DAL="#003594",DEN="#FB4F14",
  DET="#0076B6",GB="#203731",HOU="#03202F",IND="#002C5F",JAX="#006778",
  KC="#E31837",LAC="#0080C6",LAR="#003594",LV="#A5ACAF",MIA="#008E97",
  MIN="#4F2683",NE="#002244",NO="#D3BC8D",NYG="#0B2265",NYJ="#125740",
  PHI="#004C54",PIT="#FFB612",SEA="#002244",SF="#AA0000",TB="#D50A0A",
  TEN="#0C2340",WAS="#773141",FA="#555555")
nfl2 <- c(ARI="#FFB612",ATL="#000000",BAL="#9E7C0C",BUF="#C60C30",CAR="#000000",
  CHI="#C83803",CIN="#000000",CLE="#FF3C00",DAL="#869397",DEN="#002244",
  DET="#B0B7BC",GB="#FFB612",HOU="#C9243F",IND="#A2AAAD",JAX="#D7A22A",
  KC="#FFB81C",LAC="#FFC20E",LAR="#FFA300",LV="#000000",MIA="#FC4C02",
  MIN="#FFC62F",NE="#C60C30",NO="#101820",NYG="#A71930",NYJ="#000000",
  PHI="#A5ACAF",PIT="#101820",SEA="#69BE28",SF="#B3995D",TB="#FF7900",
  TEN="#4B92DB",WAS="#FFB612",FA="#888888")
gc1 <- function(t) { v<-nfl1[t]; if(is.na(v)) "#555555" else v }
gc2 <- function(t) { v<-nfl2[t]; if(is.na(v)) "#888888" else v }

# ---- Load data ----
raw <- fromJSON(params$data_path, simplifyVector=FALSE)

roster_df <- bind_rows(lapply(names(raw$roster_map), function(id) {
  r <- raw$roster_map[[id]]
  tibble(roster_id=id, display_name=r$display_name, team_name=r$team_name,
         wins=r$wins, losses=r$losses, fpts=r$fpts, fpts_against=r$fpts_against)
}))

# owner_id -> display_name for trade creator lookup
owner_to_disp <- setNames(roster_df$display_name,
  sapply(names(raw$roster_map), function(id) raw$roster_map[[id]]$owner_id))

players_df <- bind_rows(lapply(names(raw$players), function(pid) {
  p <- raw$players[[pid]]
  tibble(player_id=pid, full_name=p$full_name, position=p$position,
         team=p$team, search_rank=p$search_rank)
}))

draft_df <- bind_rows(lapply(raw$draft_picks, function(p) {
  tibble(pick_no=p$pick_no, round=p$round, draft_slot=p$draft_slot,
         player_id=p$player_id, roster_id=p$roster_id,
         team_name=p$team_name, display_name=p$display_name,
         player_name=p$player_name, position=p$position, nfl_team=p$nfl_team)
}))

# Roster positions (for optimal lineup)
roster_pos <- as.character(unlist(raw$roster_positions %||% list()))
starter_slots <- roster_pos[!roster_pos %in% c("BN","IR")]
n_qb  <- sum(starter_slots=="QB");  n_rb <- sum(starter_slots=="RB")
n_wr  <- sum(starter_slots=="WR");  n_te <- sum(starter_slots=="TE")
n_k   <- sum(starter_slots=="K");   n_def<- sum(starter_slots=="DEF")
n_flex<- sum(starter_slots=="FLEX")
flex_pos <- c("RB","WR","TE")

# ---- Load data ----
# player_weekly_pts pre-computed by fetchSleeperData.py:
# matchup players_points (authoritative for rostered players) +
# gap-filled FA player stats from Sleeper /stats/nfl/regular/2025/{wk}
player_weekly_pts <- raw$player_weekly_pts

player_season_pts <- lapply(player_weekly_pts, function(wks) sum(unlist(wks)))

player_pts_df <- tibble(
  player_id=names(player_season_pts),
  season_pts=unlist(player_season_pts)
) %>% left_join(players_df, by="player_id") %>%
  filter(!is.na(full_name), full_name!="")

# Matchup frame (all 17 weeks)
matchup_df <- bind_rows(lapply(names(raw$matchups), function(wk) {
  bind_rows(lapply(raw$matchups[[wk]], function(m) {
    tibble(week=as.integer(wk), roster_id=as.character(m$roster_id),
           matchup_id=m$matchup_id, points=m$points)
  }))
}))

# Regular-season results (weeks 1-14)
matchup_results <- matchup_df %>%
  filter(week<=14) %>%
  group_by(week, matchup_id) %>%
  filter(n()==2, !is.na(matchup_id)) %>%
  arrange(week, matchup_id, desc(points)) %>%
  mutate(result=c("W","L")) %>%
  ungroup()

# ---- Optimal lineup / sit-start accuracy ----
get_pos <- function(pid) {
  p <- raw$players[[pid]]; if(is.null(p)) "UNK" else as.character(p$position %||% "UNK")
}

optimal_lineup_pts <- function(pp_list, pos_map) {
  # pp_list: named list pid->pts; pos_map: pid->position
  pids <- names(pp_list)
  pts  <- as.numeric(unlist(pp_list))
  pos  <- sapply(pids, function(p) pos_map[[p]] %||% "UNK")
  df   <- tibble(pid=pids, pts=pts, pos=pos) %>% filter(pid!="BYE") %>% arrange(desc(pts))
  # greedy optimal: fill slots in order QB, RB*n, WR*n, TE, FLEX, K, DEF
  used <- rep(FALSE, nrow(df))
  total <- 0
  pick_best <- function(positions, n) {
    count <- 0
    for (i in seq_len(nrow(df))) {
      if (!used[i] && df$pos[i] %in% positions) {
        total <<- total + df$pts[i]; used[i] <<- TRUE; count <- count+1
        if (count==n) break
      }
    }
  }
  pick_best("QB",  n_qb);  pick_best("RB",  n_rb)
  pick_best("WR",  n_wr);  pick_best("TE",  n_te)
  pick_best(flex_pos, n_flex)
  pick_best("K",   n_k);   pick_best("DEF", n_def)
  total
}

# Build pos_map from players data
pos_map <- setNames(
  lapply(names(raw$players), function(pid) as.character(raw$players[[pid]]$position %||% "UNK")),
  names(raw$players)
)

sit_start_df <- bind_rows(lapply(names(raw$matchups), function(wk) {
  bind_rows(lapply(raw$matchups[[wk]], function(m) {
    rid   <- as.character(m$roster_id)
    starters <- as.character(unlist(m$starters %||% list()))
    pp    <- m$players_points
    if (length(starters)==0 || length(pp)==0) return(NULL)
    actual_pts  <- sum(as.numeric(sapply(starters, function(p) pp[[p]] %||% 0)))
    optimal_pts <- optimal_lineup_pts(pp, pos_map)
    tibble(week=as.integer(wk), roster_id=rid,
           actual=actual_pts, optimal=optimal_pts,
           efficiency=if(optimal_pts>0) actual_pts/optimal_pts else NA_real_)
  }))
})) %>%
  left_join(roster_df %>% select(roster_id, team_name, display_name), by="roster_id")

# ---- Post-transaction pts helper ----
pts_from_week <- function(pid, from_week) {
  wks <- player_weekly_pts[[pid]]
  if (is.null(wks)) return(0)
  sum(unlist(wks[as.character(seq(from_week, 17))]), na.rm=TRUE)
}

eval_txns <- function(txn_list) {
  rows <- lapply(txn_list, function(t) {
    wk   <- as.integer(t$week)
    rids <- as.character(unlist(t$roster_ids))
    if (length(rids)==0) return(NULL)
    inner <- lapply(rids, function(rid) {
      rec_pids  <- as.character(unlist(t$adds[[rid]]  %||% character(0)))
      gave_pids <- as.character(unlist(t$drops[[rid]] %||% character(0)))
      rec_pids  <- rec_pids[!is.na(rec_pids)  & nchar(rec_pids)>0]
      gave_pids <- gave_pids[!is.na(gave_pids) & nchar(gave_pids)>0]
      rec_pts  <- if(length(rec_pids)>0)  sum(vapply(rec_pids,  pts_from_week, numeric(1), from_week=wk)) else 0
      gave_pts <- if(length(gave_pids)>0) sum(vapply(gave_pids, pts_from_week, numeric(1), from_week=wk)) else 0
      rec_pos <- if(length(rec_pids)>0)
        paste(vapply(rec_pids, function(p){ pl<-raw$players[[p]]; if(is.null(pl)) "UNK" else as.character(pl$position %||% "UNK") }, character(1)), collapse=",")
      else ""
      rec_names  <- paste(vapply(rec_pids,  function(p){pl<-raw$players[[p]];if(is.null(pl))p else as.character(pl$full_name)},character(1)),collapse=", ")
      gave_names <- paste(vapply(gave_pids, function(p){pl<-raw$players[[p]];if(is.null(pl))p else as.character(pl$full_name)},character(1)),collapse=", ")
      dp_txt <- if(length(t$draft_picks)>0) paste0("+ ",length(t$draft_picks)," pick(s)") else ""
      tibble(
        week=wk, transaction_id=as.character(t$transaction_id), roster_id=rid,
        team_name  ={tm<-roster_df$team_name[roster_df$roster_id==rid];  if(length(tm)==0) rid else tm[1]},
        display_name={dn<-roster_df$display_name[roster_df$roster_id==rid];if(length(dn)==0) rid else dn[1]},
        received   =paste(c(rec_names,dp_txt)[nchar(c(rec_names,dp_txt))>0],collapse=" "),
        gave=gave_names,
        rec_position=rec_pos,
        received_pts=as.numeric(rec_pts), gave_pts=as.numeric(gave_pts),
        net_pts=as.numeric(rec_pts)-as.numeric(gave_pts)
      )
    })
    bind_rows(Filter(Negate(is.null), inner))
  })
  bind_rows(Filter(Negate(is.null), rows))
}

trades_raw  <- raw$trades  %||% list()
waivers_raw <- raw$waivers %||% list()
trade_sum   <- if(length(trades_raw)>0)  eval_txns(trades_raw)  else tibble()
waiver_sum  <- if(length(waivers_raw)>0) eval_txns(waivers_raw) else tibble()

# ---- Waiver position normalization ----
# A QB pickup scores ~4x more raw pts than a WR just by position norms.
# For each waiver row, subtract the median received_pts for that position
# across ALL waiver adds of that position. net_pts_adj = how much better
# (or worse) your add was vs a replacement-level add at the same position.
if (nrow(waiver_sum) > 0 && "rec_position" %in% names(waiver_sum)) {
  pos_median_waiver <- waiver_sum %>%
    filter(nchar(rec_position) > 0, rec_position != "UNK", received_pts > 0) %>%
    # Use only the primary position (first if comma-separated multi-player txn)
    mutate(primary_pos = str_extract(rec_position, "^[^,]+")) %>%
    group_by(primary_pos) %>%
    summarise(pos_med_rec = median(received_pts, na.rm=TRUE), .groups="drop")

  waiver_sum <- waiver_sum %>%
    mutate(primary_pos = str_extract(rec_position, "^[^,]+")) %>%
    left_join(pos_median_waiver, by="primary_pos") %>%
    mutate(
      pos_med_rec  = replace_na(pos_med_rec, 0),
      # Adjusted net: pts above position median for the add (drop side removed —
      # position normalization on the received side already makes this apples-to-apples)
      net_pts_adj  = received_pts - pos_med_rec
    )
} else {
  waiver_sum <- waiver_sum %>% mutate(net_pts_adj = net_pts)
}

# Trade verdicts with villain/victim
trade_verdicts <- if(nrow(trade_sum)>0) {
  creator_map <- setNames(
    sapply(trades_raw, function(t) owner_to_disp[as.character(t$creator)] %||% as.character(t$creator)),
    sapply(trades_raw, function(t) as.character(t$transaction_id))
  )
  trade_sum %>%
    group_by(transaction_id, week) %>%
    mutate(
      winner_dn = display_name[which.max(net_pts)],
      loser_dn  = display_name[which.min(net_pts)],
      winner_net= max(net_pts), loser_net=min(net_pts),
      imbalance = abs(winner_net-loser_net),
      initiator = creator_map[transaction_id]
    ) %>% ungroup()
} else tibble()

# ---- GM Score components ----
trade_mgr <- if(nrow(trade_sum)>0)
  trade_sum %>% group_by(display_name,team_name) %>%
    summarise(trade_net=sum(net_pts), n_trades=n(), .groups="drop") else
  roster_df %>% transmute(display_name, team_name, trade_net=0, n_trades=0)

waiver_mgr <- if(nrow(waiver_sum)>0)
  waiver_sum %>% group_by(display_name) %>%
    summarise(waiver_net=mean(net_pts_adj), n_waivers=n(), .groups="drop") else
  roster_df %>% transmute(display_name, waiver_net=0, n_waivers=0)

draft_voe_mgr <- draft_df %>%
  left_join(player_pts_df %>% select(player_id, season_pts), by="player_id") %>%
  mutate(season_pts=replace_na(season_pts,0)) %>%
  group_by(round) %>% mutate(round_med=median(season_pts,na.rm=TRUE)) %>% ungroup() %>%
  mutate(voe=season_pts-round_med) %>%
  group_by(display_name, team_name=team_name) %>%
  summarise(draft_voe=sum(voe,na.rm=TRUE), .groups="drop")

sit_start_mgr <- sit_start_df %>%
  filter(week<=14) %>%
  group_by(display_name, team_name) %>%
  summarise(avg_eff=mean(efficiency,na.rm=TRUE), .groups="drop") %>%
  mutate(eff_z=(avg_eff-mean(avg_eff,na.rm=TRUE))/sd(avg_eff,na.rm=TRUE))

gm_df <- roster_df %>% select(display_name, team_name) %>%
  left_join(trade_mgr  %>% select(display_name, trade_net, n_trades),  by="display_name") %>%
  left_join(waiver_mgr %>% select(display_name, waiver_net, n_waivers),by="display_name") %>%
  left_join(draft_voe_mgr %>% select(display_name, draft_voe), by="display_name") %>%
  left_join(sit_start_mgr %>% select(display_name, avg_eff, eff_z),   by="display_name") %>%
  mutate(
    across(c(trade_net,waiver_net,draft_voe,avg_eff,eff_z), ~replace_na(.,0)),
    across(c(n_trades, n_waivers), ~replace_na(as.integer(.),0L)),
    # Z-score each component then combine
    z_trade  = (trade_net   - mean(trade_net,  na.rm=TRUE)) / (sd(trade_net,  na.rm=TRUE)+1),
    z_waiver = (waiver_net  - mean(waiver_net, na.rm=TRUE)) / (sd(waiver_net, na.rm=TRUE)+1),
    z_draft  = (draft_voe   - mean(draft_voe,  na.rm=TRUE)) / (sd(draft_voe,  na.rm=TRUE)+1),
    gm_score = z_trade + z_waiver + z_draft + eff_z
  ) %>%
  arrange(desc(gm_score))
```

<meta name="viewport" content="width=device-width, initial-scale=1.0">
<style>
@page { size: 11in 14in; margin: 0.6in 0.5in; }
* { box-sizing: border-box; }
body { background-color: #0A1628; color: #FFFFFF; font-family: 'Segoe UI', Tahoma, sans-serif; max-width: 100%; overflow-x: hidden; padding: 0 8px; }
h1 { color: #FFFFFF; border-bottom: 2px solid #4A9EDB; padding-bottom: 8px; font-size: clamp(1.2rem, 4vw, 2rem); }
h2, h3, h4 { color: #4A9EDB; font-size: clamp(1rem, 3vw, 1.5rem); }
.section-header { background: #112244; border-left: 4px solid #4A9EDB; padding: 8px 16px; margin: 24px 0 12px 0; border-radius: 0 4px 4px 0; }
.section-header h2 { color: #FFFFFF; margin: 0; }
hr { border-color: #1A2E50; }
table { background: #0D1F3C; color: #FFFFFF; border-collapse: collapse; width: 100%; margin-bottom: 16px; table-layout: auto; word-wrap: break-word; font-size: clamp(0.65rem, 2vw, 0.9rem); }
th { background: #112244; color: #4A9EDB; padding: 8px 6px; border-bottom: 2px solid #4A9EDB; text-align: left; }
td { padding: 6px 6px; border-bottom: 1px solid #1A2E50; }
tr:hover td { background: #152A4A; }
.table-responsive { width: 100%; overflow-x: auto; -webkit-overflow-scrolling: touch; }
img { max-width: 85% !important; width: 85% !important; height: auto !important; display: block; margin: 0 auto; }
figure, .figure { width: 85% !important; max-width: 85% !important; margin: 0 auto 16px auto; }
.plot-container, p > img { width: 85%; margin: 0 auto; }
blockquote { border-left: 3px solid #4A9EDB; padding-left: 12px; color: #8AAAC8; margin: 8px 0; font-size: clamp(0.8rem, 2.5vw, 1rem); }
pre.bracket { font-family: 'Courier New', monospace; background: #0D1F3C; padding: 16px; border-radius: 6px; line-height: 2; color: #FFFFFF; border-left: 3px solid #4A9EDB; white-space: pre; overflow-x: auto; font-size: clamp(0.6rem, 2vw, 0.9rem); }
@media (max-width: 600px) {
  img { max-width: 100% !important; width: 100% !important; }
  figure, .figure { width: 100% !important; max-width: 100% !important; }
  .plot-container, p > img { width: 100%; }
  body { padding: 0 4px; }
}
</style>

# Room 40 - 2025 Fantasy Football Season Wrapped

---

## Final Standings

```{r standings-table}
# Playoff finish lookup (determined from bracket data)
finish_map <- c(
  LeChuckski  = "1st - Champion",
  comfyboxers = "2nd - Runner-up",
  jhcv        = "3rd Place",
  MullyMammoth= "4th Place"
)

roster_df %>%
  mutate(
    finish_rank = case_when(
      display_name == "LeChuckski"  ~ 1,
      display_name == "comfyboxers" ~ 2,
      display_name == "jhcv"        ~ 3,
      display_name == "MullyMammoth"~ 4,
      TRUE                          ~ 4L + rank(desc(wins + fpts/10000), ties.method="first")[match(display_name, display_name)]
    )
  ) %>%
  arrange(finish_rank) %>%
  mutate(
    Rank   = row_number(),
    Record = paste0(wins,"-",losses),
    `Pts For`    = round(fpts, 1),
    `Pts Against`= round(fpts_against, 1),
    Finish = ifelse(display_name %in% names(finish_map), finish_map[display_name], paste0("RS #",rank(desc(wins+fpts/10000), ties.method="first")[match(display_name,display_name)]))
  ) %>%
  select(Rank, Team=team_name, Manager=display_name, Record, `Pts For`, `Pts Against`, Finish) %>%
  knitr::kable(align=c("c","l","l","c","r","r","l"))
```

> LeChuckski won the championship (156.1-109.6 over comfyboxers in Week 17).

---

## Playoff Bracket

```{r playoff-bracket, fig.height=7, fig.width=10}
# Build bracket data from matchup results
get_bracket_week <- function(wk) {
  matchup_df %>% filter(week==wk, !is.na(matchup_id)) %>%
    left_join(roster_df %>% select(roster_id, display_name, team_name), by="roster_id") %>%
    group_by(matchup_id) %>%
    arrange(desc(points)) %>%
    summarise(
      w_name=first(display_name), w_pts=first(points),
      l_name=last(display_name),  l_pts=last(points),
      .groups="drop"
    ) %>% arrange(matchup_id)
}

w15 <- get_bracket_week(15)
w16 <- get_bracket_week(16)
w17 <- get_bracket_week(17)

# Build a visual bracket as a ggplot
# Layout: 3 columns (weeks 15, 16, 17), rows = matchups
bracket_data <- bind_rows(
  w15 %>% mutate(round="Wk 15\nFirst Round",  round_x=1, matchup_y=as.numeric(matchup_id)*2),
  w16 %>% mutate(round="Wk 16\nSemifinals",   round_x=2, matchup_y=as.numeric(matchup_id)*2),
  w17 %>% mutate(round="Wk 17\nChampionship", round_x=3, matchup_y=as.numeric(matchup_id)*2)
)

# Draw as a table-style ggplot
ggplot() +
  # Background panels per round
  annotate("rect", xmin=0.55, xmax=1.45, ymin=-Inf, ymax=Inf, fill=bg_card, alpha=0.5) +
  annotate("rect", xmin=1.55, xmax=2.45, ymin=-Inf, ymax=Inf, fill=bg_card, alpha=0.5) +
  annotate("rect", xmin=2.55, xmax=3.45, ymin=-Inf, ymax=Inf, fill=bg_card, alpha=0.5) +
  # Round labels
  annotate("text", x=1, y=11, label="Wk 15 - First Round", color=col_blue, size=4.5, fontface="bold") +
  annotate("text", x=2, y=11, label="Wk 16 - Semifinals",  color=col_blue, size=4.5, fontface="bold") +
  annotate("text", x=3, y=11, label="Wk 17 - Finals",       color=col_blue, size=4.5, fontface="bold") +
  # Week 15 matchups
  {rows15 <- w15; lapply(seq_len(nrow(rows15)), function(i) {
    r <- rows15[i,]; y_base <- (5-i)*2
    list(
      annotate("rect",  xmin=0.6,xmax=1.4, ymin=y_base-0.45,ymax=y_base+0.45, fill=col_green,  alpha=0.25, color=col_green,  linewidth=0.4),
      annotate("rect",  xmin=0.6,xmax=1.4, ymin=y_base-1.35,ymax=y_base-0.55, fill=col_red,    alpha=0.15, color=col_red,    linewidth=0.4),
      annotate("text",  x=0.65, y=y_base,    label=paste0(r$w_name," (",round(r$w_pts,1),")"), hjust=0, color=col_white, size=3.1, fontface="bold"),
      annotate("text",  x=0.65, y=y_base-0.9,label=paste0(r$l_name," (",round(r$l_pts,1),")"), hjust=0, color=col_dim,   size=3.0)
    )
  })} +
  # Week 16 matchups
  {rows16 <- w16; lapply(seq_len(nrow(rows16)), function(i) {
    r <- rows16[i,]; y_base <- (3.5-i)*2
    list(
      annotate("rect",  xmin=1.6,xmax=2.4, ymin=y_base-0.45,ymax=y_base+0.45, fill=col_green, alpha=0.25, color=col_green, linewidth=0.4),
      annotate("rect",  xmin=1.6,xmax=2.4, ymin=y_base-1.35,ymax=y_base-0.55, fill=col_red,   alpha=0.15, color=col_red,   linewidth=0.4),
      annotate("text",  x=1.65, y=y_base,    label=paste0(r$w_name," (",round(r$w_pts,1),")"), hjust=0, color=col_white, size=3.1, fontface="bold"),
      annotate("text",  x=1.65, y=y_base-0.9,label=paste0(r$l_name," (",round(r$l_pts,1),")"), hjust=0, color=col_dim,   size=3.0)
    )
  })} +
  # Week 17 matchups
  {rows17 <- w17; lapply(seq_len(nrow(rows17)), function(i) {
    r <- rows17[i,]; y_base <- (2.5-i)*2.5
    crown <- if(i==1) " [CHAMP]" else ""
    list(
      annotate("rect",  xmin=2.6,xmax=3.4, ymin=y_base-0.45,ymax=y_base+0.45, fill=ifelse(i==1,col_gold,col_green), alpha=0.25, color=ifelse(i==1,col_gold,col_green), linewidth=0.5),
      annotate("rect",  xmin=2.6,xmax=3.4, ymin=y_base-1.35,ymax=y_base-0.55, fill=col_red, alpha=0.15, color=col_red, linewidth=0.4),
      annotate("text",  x=2.65, y=y_base,    label=paste0(r$w_name,crown," (",round(r$w_pts,1),")"), hjust=0, color=ifelse(i==1,col_gold,col_white), size=3.1, fontface="bold"),
      annotate("text",  x=2.65, y=y_base-0.9,label=paste0(r$l_name," (",round(r$l_pts,1),")"),       hjust=0, color=col_dim,   size=3.0)
    )
  })} +
  scale_x_continuous(limits=c(0.5,3.5), breaks=NULL) +
  scale_y_continuous(limits=c(-2, 12),  breaks=NULL) +
  labs(title="2025 Room 40 Playoff Bracket", x=NULL, y=NULL) +
  tw() + theme(panel.grid=element_blank(), axis.text=element_blank())
```

---

<div class="section-header"><h2>Section 1: The Draft</h2></div>

```{r draft-adp-scatter, fig.height=7}
draft_plot <- draft_df %>%
  left_join(player_pts_df %>% select(player_id, season_pts), by="player_id") %>%
  mutate(season_pts=replace_na(season_pts,0),
         c1=sapply(nfl_team, gc1), c2=sapply(nfl_team, gc2),
         label=ifelse(round<=4|season_pts>300|(pick_no>60&season_pts>200), player_name, NA))

ggplot(draft_plot, aes(x=pick_no, y=season_pts)) +
  geom_hline(yintercept=median(draft_plot$season_pts,na.rm=TRUE),
             color=col_dim, linetype="dashed", linewidth=0.5) +
  # Use formula=y~x with scale_x_log10() — the scale handles the log transform,
  # so formula=y~log(x) would double-log and produce NaN/Inf, hiding the line
  stat_smooth(method="lm", formula=y~x, se=TRUE, geom="ribbon",
              fill=col_blue, alpha=0.22) +
  stat_smooth(method="lm", formula=y~x, se=FALSE, geom="line",
              color=col_blue, linewidth=1.4) +
  geom_point(aes(fill=c1, color=c2), size=3.5, alpha=0.92, shape=21, stroke=1.2) +
  scale_fill_identity() + scale_color_identity() +
  scale_x_log10(breaks=c(1,5,10,20,40,80,140), labels=c("1","5","10","20","40","80","140")) +
  geom_text_repel(aes(label=label), color=col_white, size=2.8,
                  max.overlaps=25, segment.color=col_dim, segment.size=0.3,
                  box.padding=0.35, na.rm=TRUE) +
  labs(title="Draft Pick vs Season Fantasy Points",
       subtitle="Log x-axis. Blue band = regression. Dots = NFL team colors.",
       x="Overall Draft Pick (log scale)", y="Total Fantasy Points") +
  tw()
```

```{r draft-vs-adp, fig.height=6}
# ---- League vs Industry ADP ----
adp_raw <- raw$adp_map %||% list()

clean_for_adp <- function(n) {
  n <- str_to_lower(str_trim(n))
  n <- str_replace(n, "\\s+(jr\\.?|sr\\.?|ii|iii|iv)$", "")
  n
}

adp_df <- draft_df %>%
  filter(!position %in% c("K","DEF")) %>%
  mutate(
    name_key   = clean_for_adp(player_name),
    adp        = as.numeric(sapply(name_key, function(n) adp_raw[[n]] %||% NA_real_)),
    reach      = adp - pick_no,   # positive = value (drafted later than ADP), negative = reach
    reach_lbl  = ifelse(reach >= 0,
                        paste0("+", round(reach, 1)),
                        as.character(round(reach, 1)))
  ) %>%
  filter(!is.na(adp))

if (nrow(adp_df) > 0) {
  # Plot 1: Pick # vs ADP scatter — above diagonal = reached, below = value
  ggplot(adp_df, aes(x=pick_no, y=adp)) +
    geom_abline(slope=1, intercept=0, color=col_white, linetype="dashed", linewidth=0.6) +
    geom_point(aes(fill=reach, color=reach), size=3, alpha=0.85, shape=21, stroke=0.8) +
    scale_fill_gradient2(low=col_green, mid=col_gold, high=col_red,
                         midpoint=0, name="Value\n(+ = value, - = reach)") +
    scale_color_gradient2(low=col_green, mid=col_gold, high=col_red,
                          midpoint=0, guide="none") +
    geom_text_repel(
      data=adp_df %>% filter(abs(reach) > 15),
      aes(label=paste0(player_name, " (", round(reach,0), ")")),
      color=col_white, size=2.6, segment.color=col_dim, segment.size=0.3,
      max.overlaps=20, box.padding=0.3
    ) +
    labs(title="Room 40 Draft Pick vs Industry ADP",
         subtitle="Dashed line = perfect consensus alignment. Green = value (drafted later than ADP), red = reach.",
         x="Room 40 Pick #", y="Industry ADP (FantasyPros Half-PPR)") +
    tw() + theme(legend.position="right")
} else {
  cat("ADP data not available — re-run /nfl fantasywrapped to fetch fresh data.\n")
}
```

```{r draft-sharpness, fig.height=5}
if (exists("adp_df") && nrow(adp_df) > 0) {
  # Per-manager reach/value summary
  mgr_adp <- adp_df %>%
    group_by(display_name, team_name) %>%
    summarise(
      avg_reach   = mean(reach, na.rm=TRUE),
      n_picks     = n(),
      n_value     = sum(reach > 5, na.rm=TRUE),
      n_reach     = sum(reach < -5, na.rm=TRUE),
      .groups="drop"
    ) %>% arrange(desc(avg_reach))

  ggplot(mgr_adp, aes(x=fct_reorder(team_name, avg_reach), y=avg_reach, fill=avg_reach)) +
    geom_col(alpha=0.9) +
    geom_hline(yintercept=0, color=col_white, linewidth=0.5) +
    geom_text(aes(label=paste0(ifelse(avg_reach>=0,"+",""), round(avg_reach,1),
                               " (", n_picks, " picks)")),
              hjust=ifelse(mgr_adp$avg_reach>=0,-0.08,1.08),
              color=col_white, size=3.3) +
    scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                         midpoint=0, guide="none") +
    scale_y_continuous(expand=expansion(mult=c(0.15,0.2))) +
    coord_flip() +
    labs(title="Draft Sharpness by Manager",
         subtitle="Avg (industry ADP - pick #). Positive = consistently got value vs consensus, negative = reached.",
         x=NULL, y="Avg ADP Value (+= drafted later than consensus)") +
    tw()
}
```

```{r draft-voe, fig.height=6}
round_med <- draft_plot %>% group_by(round) %>%
  summarise(rmed=median(season_pts,na.rm=TRUE),.groups="drop")

voe_df <- draft_plot %>% left_join(round_med,by="round") %>%
  mutate(voe=season_pts-rmed, bar_color=ifelse(voe>=0,col_green,col_red)) %>%
  arrange(desc(voe))

voe_plot <- bind_rows(slice_head(voe_df,n=15),slice_tail(voe_df,n=15)) %>%
  distinct(player_name,.keep_all=TRUE) %>%
  mutate(
    owner_label = ifelse(!is.na(display_name) & nchar(display_name)>0,
                         paste0(player_name, " (", display_name, ")"),
                         player_name)
  )

ggplot(voe_plot, aes(x=reorder(owner_label,voe), y=voe, fill=bar_color)) +
  geom_col(alpha=0.9) + scale_fill_identity() + coord_flip() +
  geom_hline(yintercept=0, color=col_white, linewidth=0.5) +
  geom_text(aes(label=paste0(ifelse(voe>=0,"+",""),round(voe,0)),
                hjust=ifelse(voe>=0,-0.1,1.1)), color=col_white, size=2.8) +
  scale_y_continuous(expand=expansion(mult=c(0.12,0.12))) +
  labs(title="Draft Value Over Expected - Top 15 Steals & Busts",
       subtitle="Points above/below round median. Green = steal, red = bust. Owner shown in parentheses.",
       x=NULL, y="Points vs Round Median") +
  tw() + theme(axis.text.y=element_text(size=9, color=col_white))
```

```{r draft-voe-by-team, fig.height=5, fig.width=10}
# Per-team per-player VOE facet grid — top 4 / mid 4 / bottom 4 by cumulative VOE
team_voe_order <- draft_voe_mgr %>% arrange(desc(draft_voe)) %>% pull(team_name)

# Join VOE data with team ordering
voe_team_df <- voe_df %>%
  mutate(
    tier = case_when(
      team_name %in% team_voe_order[1:4]  ~ "Top Drafters",
      team_name %in% team_voe_order[5:8]  ~ "Mid Drafters",
      TRUE                                 ~ "Bottom Drafters"
    ),
    tier = factor(tier, levels=c("Top Drafters","Mid Drafters","Bottom Drafters")),
    team_name = factor(team_name, levels=team_voe_order)
  )

make_team_voe_plot <- function(teams_subset) {
  df <- voe_team_df %>% filter(team_name %in% teams_subset) %>%
    mutate(team_name = factor(team_name, levels=teams_subset))
  ggplot(df, aes(x=reorder(player_name, -voe), y=voe, fill=voe)) +
    geom_col(alpha=0.9) +
    geom_hline(yintercept=0, color=col_white, linewidth=0.4) +
    scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                         midpoint=0, guide="none") +
    scale_y_continuous(expand=expansion(mult=c(0.1,0.15))) +
    facet_wrap(~team_name, nrow=1, scales="free_x") +
    labs(x=NULL, y="VOE") +
    tw() + theme(
      axis.text.x  = element_text(size=6, color=col_white, angle=45, hjust=1),
      axis.text.y  = element_text(size=7),
      strip.text   = element_text(size=8, face="bold"),
      plot.margin  = margin(2,4,2,4)
    )
}

make_team_voe_plot(team_voe_order[1:4])
```

```{r draft-voe-by-team-mid, fig.height=5, fig.width=10}
make_team_voe_plot(team_voe_order[5:8])
```

```{r draft-voe-by-team-bot, fig.height=5, fig.width=10}
make_team_voe_plot(team_voe_order[9:12])
```

```{r draft-voe-manager, fig.height=5}
ggplot(draft_voe_mgr, aes(x=fct_reorder(team_name,draft_voe),y=draft_voe,
                            fill=draft_voe)) +
  geom_col(alpha=0.9) +
  geom_hline(yintercept=0, color=col_white, linewidth=0.5) +
  geom_text(aes(label=paste0(ifelse(draft_voe>=0,"+",""),round(draft_voe,1)),
                hjust=ifelse(draft_voe>=0,-0.1,1.1)), color=col_white, size=3.5) +
  scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                       midpoint=0, guide="none") +
  scale_y_continuous(expand=expansion(mult=c(0.15,0.15))) +
  coord_flip() +
  labs(title="Cumulative Draft VOE by Manager",
       subtitle="Sum of (player pts - round median) across all picks. Who drafted better?",
       x=NULL, y="Total VOE") +
  tw()
```

---

<div class="section-header"><h2>Section 2: Position Leaders</h2></div>

```{r pos-leaders-setup}
# End-of-season roster ownership: find the last week each player appeared
# on a roster, and use that manager as their "owner"
last_week_ownership <- bind_rows(lapply(names(raw$matchups), function(wk) {
  bind_rows(lapply(raw$matchups[[wk]], function(m) {
    pids <- as.character(unlist(m$players %||% list()))
    if(length(pids)==0) return(NULL)
    tibble(week=as.integer(wk), roster_id=as.character(m$roster_id), player_id=pids)
  }))
})) %>%
  left_join(roster_df %>% select(roster_id, fantasy_team=team_name, fantasy_manager=display_name),
            by="roster_id") %>%
  group_by(player_id) %>%
  slice_max(week, n=1, with_ties=FALSE) %>%
  ungroup() %>%
  select(player_id, fantasy_team, fantasy_manager)

make_pos_bar <- function(pos, n, title_label) {
  df <- player_pts_df %>% filter(position==pos) %>% arrange(desc(season_pts)) %>%
    slice_head(n=n) %>% left_join(last_week_ownership, by="player_id") %>%
    mutate(c1=sapply(team,gc1), c2=sapply(team,gc2),
           owner_label=ifelse(!is.na(fantasy_manager),
                              paste0(round(season_pts,1)," | ",fantasy_manager),
                              round(season_pts,1)))
  ggplot(df, aes(x=season_pts, y=fct_reorder(full_name,season_pts))) +
    geom_col(aes(fill=c1), alpha=0.92, width=0.8) +
    geom_col(aes(fill=c2), alpha=0, color=df$c2, linewidth=0.9, width=0.8) +
    geom_text(aes(label=owner_label), hjust=-0.05, color=col_white, size=2.9) +
    scale_fill_identity() + scale_x_continuous(expand=expansion(mult=c(0,0.3))) +
    labs(title=title_label,
         subtitle=paste("Top",n,"| label: pts | Room 40 owner (end of season)"),
         x="Fantasy Points", y=NULL) +
    tw() + theme(axis.text.y=element_text(color=col_white, size=9))
}
```

```{r pos-row1, fig.height=4, fig.width=10}
library(gridExtra)
grid.arrange(
  make_pos_bar("QB",5,"Quarterback Leaders"),
  make_pos_bar("RB",5,"Running Back Leaders"),
  ncol=2
)
```
```{r pos-row2, fig.height=4, fig.width=10}
grid.arrange(
  make_pos_bar("WR",5,"Wide Receiver Leaders"),
  make_pos_bar("TE",5,"Tight End Leaders"),
  ncol=2
)
```
```{r pos-row3, fig.height=4, fig.width=10}
grid.arrange(
  make_pos_bar("DEF",5,"Defense/ST Leaders"),
  make_pos_bar("K",5,"Kicker Leaders"),
  ncol=2
)
```

---

<div class="section-header"><h2>Section 3: High & Low Scores</h2></div>

```{r high-low-teams, fig.height=5}
team_weekly <- matchup_df %>%
  left_join(roster_df %>% select(roster_id,team_name,display_name), by="roster_id") %>%
  filter(!is.na(points), points>0)

bind_rows(
  team_weekly %>% arrange(desc(points)) %>% slice_head(n=5) %>%
    mutate(lbl=paste0(team_name,"\nWk",week,": ",round(points,1)), type="Top 5"),
  team_weekly %>% arrange(points) %>% slice_head(n=5) %>%
    mutate(lbl=paste0(team_name,"\nWk",week,": ",round(points,1)), type="Bottom 5")
) %>%
  ggplot(aes(x=fct_reorder(lbl,points), y=points,
             fill=ifelse(type=="Top 5",col_green,col_red))) +
  geom_col(alpha=0.9) +
  geom_text(aes(label=round(points,1),hjust=ifelse(type=="Top 5",-0.1,1.1)),
            color=col_white, size=3.2) +
  scale_fill_identity() + scale_y_continuous(expand=expansion(mult=c(0.05,0.15))) +
  coord_flip() + facet_wrap(~type, scales="free") +
  labs(title="Single-Week Team Score Records", x=NULL, y="Points") +
  tw() + theme(axis.text.y=element_text(color=col_white, size=8))
```

```{r high-low-players, fig.height=5}
# Build player weekly rows with fantasy team owner that week
# (who had them on their active roster - starters or bench)
roster_ownership <- bind_rows(lapply(names(raw$matchups), function(wk) {
  bind_rows(lapply(raw$matchups[[wk]], function(m) {
    pids <- as.character(unlist(m$players %||% list()))
    if(length(pids)==0) return(NULL)
    tibble(week=as.integer(wk), roster_id=as.character(m$roster_id), player_id=pids)
  }))
})) %>% left_join(roster_df %>% select(roster_id, team_name), by="roster_id")

player_wk_rows <- bind_rows(lapply(names(raw$matchups), function(wk) {
  bind_rows(lapply(raw$matchups[[wk]], function(m) {
    pp <- m$players_points
    if(length(pp)==0) return(NULL)
    tibble(week=as.integer(wk), player_id=names(pp), pts=as.numeric(unlist(pp)))
  }))
})) %>% filter(player_id!="BYE", pts>0) %>%
  left_join(players_df %>% select(player_id,full_name,position,team), by="player_id") %>%
  left_join(roster_ownership %>% distinct(week,player_id,.keep_all=TRUE) %>%
              select(week,player_id,fantasy_team=team_name), by=c("week","player_id"))

bind_rows(
  player_wk_rows %>% arrange(desc(pts)) %>% filter(!is.na(full_name)) %>% slice_head(n=5) %>%
    mutate(lbl=paste0(full_name," (",position,")\n",
                      ifelse(is.na(fantasy_team),"",paste0(fantasy_team," | ")),
                      "Wk",week,": ",round(pts,1)), type="Top 5"),
  player_wk_rows %>% arrange(pts) %>% filter(!is.na(full_name)) %>% slice_head(n=5) %>%
    mutate(lbl=paste0(full_name," (",position,")\n",
                      ifelse(is.na(fantasy_team),"",paste0(fantasy_team," | ")),
                      "Wk",week,": ",round(pts,1)), type="Bottom 5")
) %>%
  ggplot(aes(x=fct_reorder(lbl,pts), y=pts,
             fill=ifelse(type=="Top 5",col_green,col_red))) +
  geom_col(alpha=0.9) +
  geom_text(aes(label=round(pts,1),hjust=ifelse(type=="Top 5",-0.1,1.1)),
            color=col_white, size=3.2) +
  scale_fill_identity() + scale_y_continuous(expand=expansion(mult=c(0.05,0.15))) +
  coord_flip() + facet_wrap(~type, scales="free") +
  labs(title="Single-Week Player Score Records",
       subtitle="Fantasy team shown on label",
       x=NULL, y="Points") +
  tw() + theme(axis.text.y=element_text(color=col_white, size=8))
```

---

<div class="section-header"><h2>Section 4: Sit / Start Accuracy</h2></div>

```{r sit-start-plot, fig.height=5}
ss_mgr_rs <- sit_start_df %>%
  filter(week<=14) %>%
  group_by(display_name, team_name) %>%
  summarise(avg_eff=mean(efficiency,na.rm=TRUE),
            avg_left=mean(optimal-actual,na.rm=TRUE), .groups="drop") %>%
  arrange(desc(avg_eff))

ggplot(ss_mgr_rs, aes(x=fct_reorder(team_name,avg_eff), y=avg_eff*100,
                       fill=avg_eff)) +
  geom_col(alpha=0.9) +
  geom_hline(yintercept=mean(ss_mgr_rs$avg_eff)*100, color=col_white,
             linetype="dashed", linewidth=0.5) +
  geom_text(aes(label=paste0(round(avg_eff*100,1),"%"),hjust=-0.1),
            color=col_white, size=3.5) +
  scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                       midpoint=mean(ss_mgr_rs$avg_eff), guide="none") +
  scale_y_continuous(expand=expansion(mult=c(0,0.15)),
                     labels=function(x) paste0(x,"%")) +
  coord_flip() +
  labs(title="Lineup Efficiency (Sit/Start Accuracy)",
       subtitle="Actual starter pts / optimal possible pts each week (regular season). Higher = better decisions.",
       x=NULL, y="Avg Lineup Efficiency (%)") +
  tw() + theme(axis.text.y=element_text(color=col_white, size=9))
```

```{r pts-left-on-bench, fig.height=5}
ggplot(ss_mgr_rs, aes(x=fct_reorder(team_name,-avg_left), y=avg_left,
                       fill=avg_left)) +
  geom_col(alpha=0.9) +
  geom_text(aes(label=round(avg_left,1),hjust=-0.1), color=col_white, size=3.5) +
  scale_fill_gradient2(low=col_green, mid=col_gold, high=col_red,
                       midpoint=mean(ss_mgr_rs$avg_left), guide="none") +
  scale_y_continuous(expand=expansion(mult=c(0,0.15))) +
  coord_flip() +
  labs(title="Average Points Left on Bench Per Week",
       subtitle="Optimal lineup pts - actual pts. Lower = smarter decisions.",
       x=NULL, y="Avg Pts Left on Bench") +
  tw() + theme(axis.text.y=element_text(color=col_white, size=9))
```

---

<div class="section-header"><h2>Section 5: Trades</h2></div>

```{r trade-balance, fig.height=6}
if(nrow(trade_sum)>0) {
  ts <- trade_sum %>% group_by(display_name,team_name) %>%
    summarise(total_net=sum(net_pts),.groups="drop") %>% arrange(desc(total_net))
  ggplot(ts, aes(x=fct_reorder(team_name,total_net),y=total_net,fill=total_net)) +
    geom_col(alpha=0.9) + geom_hline(yintercept=0,color=col_white,linewidth=0.5) +
    geom_text(aes(label=paste0(ifelse(total_net>=0,"+",""),round(total_net,1)),
                  hjust=ifelse(total_net>=0,-0.1,1.1)), color=col_white, size=3.5) +
    scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                         midpoint=0, guide="none") +
    scale_y_continuous(expand=expansion(mult=c(0.15,0.15))) +
    coord_flip() +
    labs(title="Trade Balance by Manager",
         subtitle="Net post-trade fantasy points gained vs given away",
         x=NULL, y="Net Points (post-trade)") + tw()
}
```

```{r fleece-jobs}
if(nrow(trade_verdicts)>0) {
  unique_tv <- trade_verdicts %>%
    distinct(transaction_id, week, winner_dn, loser_dn, imbalance, initiator)

  # Fleece = initiator won (they proposed and got the better end)
  fleeces <- unique_tv %>%
    filter(winner_dn == initiator) %>%
    arrange(desc(imbalance)) %>% slice_head(n=5) %>%
    mutate(.sort_order = row_number())
  self_owns <- unique_tv %>%
    filter(loser_dn == initiator) %>%
    arrange(desc(imbalance)) %>% slice_head(n=5) %>%
    mutate(.sort_order = row_number())
}
```

#### 5 Most Egregious Fleece Jobs

```{r fleece-table}
if(nrow(trade_verdicts)>0 && nrow(fleeces)>0) {
  ft <- fleeces %>%
    left_join(trade_sum %>% select(transaction_id, roster_id, received, gave,
                                   display_name),
              by=c("transaction_id", "winner_dn"="display_name")) %>%
    group_by(transaction_id) %>% slice_head(n=1) %>% ungroup() %>%
    arrange(.sort_order) %>%
    transmute(
      `#`=.sort_order, Week=week,
      Villain=winner_dn, Victim=loser_dn,
      `Got`=ifelse(is.na(received)|received=="", "-", received),
      `Gave`=ifelse(is.na(gave)|gave=="", "-", gave),
      `Pt Swing`=paste0("+",round(imbalance,1))
    )
  knitr::kable(ft, align=c("c","c","l","l","l","l","r"))
} else cat("No trades where the proposer won by a large margin.\n")
```

#### 5 Biggest Clowns

```{r self-owns-table}
if(nrow(trade_verdicts)>0 && nrow(self_owns)>0) {
  st <- self_owns %>%
    left_join(trade_sum %>% select(transaction_id, display_name, received, gave),
              by=c("transaction_id", "loser_dn"="display_name")) %>%
    group_by(transaction_id) %>% slice_head(n=1) %>% ungroup() %>%
    arrange(.sort_order) %>%
    transmute(
      `#`=.sort_order, Week=week,
      Clown=loser_dn, `Who Benefited`=winner_dn,
      `Got`=ifelse(is.na(received)|received=="", "-", received),
      `Gave`=ifelse(is.na(gave)|gave=="", "-", gave),
      `Pt Swing`=paste0("+",round(imbalance,1))
    )
  knitr::kable(st, align=c("c","c","l","l","l","l","r"))
} else cat("No trades where the proposer lost.\n")
```

---

<div class="section-header"><h2>Section 6: Waiver Wire</h2></div>

```{r waiver-balance, fig.height=6}
if(nrow(waiver_sum)>0) {
  wm <- waiver_sum %>% group_by(display_name,team_name) %>%
    summarise(avg_net=mean(net_pts_adj), n_moves=n(), .groups="drop") %>%
    arrange(desc(avg_net))
  ggplot(wm, aes(x=fct_reorder(team_name,avg_net),y=avg_net,fill=avg_net)) +
    geom_col(alpha=0.9) + geom_hline(yintercept=0,color=col_white,linewidth=0.5) +
    geom_text(aes(label=paste0(ifelse(avg_net>=0,"+",""),round(avg_net,1),
                               " (", n_moves, " moves)"),
                  hjust=ifelse(avg_net>=0,-0.1,1.1)), color=col_white, size=3.5) +
    scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                         midpoint=0, guide="none") +
    scale_y_continuous(expand=expansion(mult=c(0.15,0.25))) +
    coord_flip() +
    labs(title="Waiver Wire Efficiency by Manager (Position-Adjusted)",
         subtitle="Avg pts above position median per waiver add. Removes QB/RB position scoring bias. Move count shown on bar.",
         x=NULL, y="Avg Net Pts per Move") + tw()
}
```

#### Top 10 Waiver Pickups by Post-Pickup Value

```{r best-pickups}
if(nrow(waiver_sum)>0) {
  best <- waiver_sum %>% filter(nchar(received)>0, received_pts>0) %>%
    arrange(desc(received_pts)) %>% slice_head(n=10) %>%
    transmute(Week=week, Manager=paste0(team_name," (",display_name,")"),
              `Player Added`=received, `Pts (rest of season)`=round(received_pts,1))
  knitr::kable(best, align=c("c","l","l","r"))
}
```

---

<div class="section-header"><h2>Section 8: Season Progression & Luck</h2></div>

```{r luck-scatter, fig.height=7}
weekly_scores <- matchup_df %>%
  filter(week<=14) %>%
  group_by(week) %>%
  mutate(n_teams=n(), score_rank=rank(points),
         expected_wins=(score_rank-1)/(n_teams-1)) %>%
  ungroup() %>%
  left_join(matchup_results %>% select(week,roster_id,matchup_id,result), by=c("week","roster_id")) %>%
  mutate(actual_win=ifelse(result=="W",1,0)) %>%
  left_join(roster_df %>% select(roster_id,team_name,display_name), by="roster_id")

luck_df <- weekly_scores %>%
  group_by(roster_id,team_name,display_name) %>%
  summarise(actual_wins=sum(actual_win,na.rm=TRUE),
            expected_wins_total=sum(expected_wins,na.rm=TRUE),
            luck=actual_wins-expected_wins_total,
            avg_pts=mean(points), .groups="drop") %>%
  arrange(desc(luck))

ggplot(luck_df, aes(x=avg_pts, y=luck)) +
  geom_hline(yintercept=0,color=col_dim,linetype="dashed") +
  geom_vline(xintercept=mean(luck_df$avg_pts),color=col_dim,linetype="dashed") +
  geom_point(aes(color=luck), size=5) +
  scale_color_gradient2(low=col_red,mid=col_dim,high=col_green,midpoint=0,name="Luck") +
  geom_text_repel(aes(label=team_name),color=col_white,size=3.2,
                  segment.color=col_dim,box.padding=0.4) +
  labs(title="Luck vs Scoring",
       subtitle="Luck = actual wins - expected wins from weekly score rank.",
       x="Avg Weekly Points", y="Luck Score") + tw()
```

```{r cumulative-wins, fig.height=8}
cumulative <- matchup_results %>%
  filter(week<=14) %>%
  left_join(roster_df %>% select(roster_id,team_name), by="roster_id") %>%
  arrange(team_name,week) %>%
  group_by(team_name) %>%
  mutate(cum_wins=cumsum(result=="W")) %>% ungroup()

team_pal <- colorRampPalette(c(col_blue,col_gold,col_green,col_red,col_dim,
  "#B87BDB","#DB875C","#5CDBCB","#DB5C8F","#8FDB5C","#5C8FDB","#DBC85C"))(12)

ggplot(cumulative, aes(x=week,y=cum_wins,color=team_name,group=team_name)) +
  geom_line(linewidth=1.2,alpha=0.9) + geom_point(size=2,alpha=0.7) +
  scale_color_manual(values=team_pal) + scale_x_continuous(breaks=1:14) +
  labs(title="Cumulative Wins by Week",subtitle="Regular season wks 1-14",
       x="Week",y="Wins",color="Team") + tw() + theme(legend.position="right")
```

```{r score-heatmap, fig.height=7}
score_heat <- matchup_df %>%
  filter(week<=14) %>%
  left_join(roster_df %>% select(roster_id,team_name), by="roster_id") %>%
  left_join(matchup_results %>% select(week,roster_id,result), by=c("week","roster_id"))

ggplot(score_heat, aes(x=week,y=fct_reorder(team_name,points,mean),fill=points)) +
  geom_tile(color=bg_dark,linewidth=0.5) +
  geom_text(aes(label=round(points,0),color=ifelse(result=="W","#FFFFFF","#7A90A8")),size=2.5) +
  scale_color_identity() +
  scale_fill_gradient2(low=col_red,mid=bg_card,high=col_green,
                       midpoint=median(score_heat$points,na.rm=TRUE),name="Points") +
  scale_x_continuous(breaks=1:14) +
  labs(title="Weekly Score Heatmap",subtitle="Green=high, red=low. White text=win.",
       x="Week",y=NULL) + tw() + theme(axis.text.y=element_text(size=9,color=col_white))
```

```{r luck-bar, fig.height=5}
ggplot(luck_df, aes(x=fct_reorder(team_name,luck),y=luck,fill=luck)) +
  geom_col(alpha=0.9) + geom_hline(yintercept=0,color=col_white,linewidth=0.5) +
  geom_text(aes(label=paste0(ifelse(luck>=0,"+",""),round(luck,1)),
                hjust=ifelse(luck>=0,-0.1,1.1)), color=col_white,size=3.5) +
  scale_fill_gradient2(low=col_red, mid=col_gold, high=col_green,
                       midpoint=0, guide="none") +
  scale_y_continuous(expand=expansion(mult=c(0.15,0.15))) +
  coord_flip() +
  labs(title="Luck Factor by Team",subtitle="Wins above/below expected",
       x=NULL,y="Luck") + tw()
```

---

<div class="section-header"><h2>Section 9: GM Score</h2></div>

```{r gm-score-plot, fig.height=6}
gm_long <- gm_df %>%
  select(team_name, display_name, z_trade, z_waiver, z_draft, eff_z) %>%
  pivot_longer(cols=c(z_trade,z_waiver,z_draft,eff_z),
               names_to="component", values_to="z") %>%
  mutate(component=recode(component,
    z_trade="Trade",z_waiver="Waivers",z_draft="Draft VOE",eff_z="Lineup Eff"))

comp_colors <- c(Trade=col_blue, Waivers=col_green, `Draft VOE`=col_gold, `Lineup Eff`="#B87BDB")

# Order: highest GM score at top (descending), so fct_reorder by ascending score
# then coord_flip puts highest at the top
gm_order <- gm_df %>% arrange(gm_score) %>% pull(team_name)

# Score label data for the total-score line/label
gm_score_ref <- gm_df %>% select(team_name, gm_score)

ggplot(gm_long, aes(x=factor(team_name, levels=gm_order), y=z, fill=component)) +
  geom_col(position="stack", alpha=0.85) +
  geom_hline(yintercept=0, color=col_white, linewidth=0.5) +
  # Total GM score marker: segment spanning the bar width at the final score value
  geom_segment(data=gm_score_ref,
               aes(x=as.numeric(factor(team_name, levels=gm_order)) - 0.42,
                   xend=as.numeric(factor(team_name, levels=gm_order)) + 0.42,
                   y=gm_score, yend=gm_score),
               inherit.aes=FALSE, color="#00FFFF", linewidth=1.2) +
  # Score label to the right of the marker
  geom_text(data=gm_score_ref,
            aes(x=factor(team_name, levels=gm_order),
                y=gm_score, label=round(gm_score, 2)),
            inherit.aes=FALSE, color="#00FFFF", size=3.2, fontface="bold",
            hjust=ifelse(gm_score_ref$gm_score >= 0, -0.25, 1.25)) +
  scale_fill_manual(values=comp_colors, name="Component") +
  coord_flip() +
  labs(title="GM Score: Composite Roster Management",
       subtitle="Stacked z-scores by component. Cyan line = composite GM Score.",
       x=NULL, y="GM Score (z-score composite)") +
  tw() + theme(legend.position="top")
```

```{r gm-table}
fmt_z <- function(z) paste0("(z=", ifelse(z>=0,"+",""), round(z,2), ")")
gm_df %>%
  mutate(Rank=row_number()) %>%
  transmute(Rank, Team=team_name, Manager=display_name,
            `Trade Net`=paste0(ifelse(trade_net>=0,"+",""),round(trade_net,1),
                               " ", fmt_z(z_trade)),
            `Waiver Net`=paste0(ifelse(waiver_net>=0,"+",""),round(waiver_net,2),
                                " ", fmt_z(z_waiver)),
            `Draft VOE`=paste0(ifelse(draft_voe>=0,"+",""),round(draft_voe,1),
                               " ", fmt_z(z_draft)),
            `Lineup Eff`=paste0(round(avg_eff*100,1),"%",
                                " ", fmt_z(eff_z)),
            `GM Score`=round(gm_score,2)) %>%
  knitr::kable(align=c("c","l","l","r","r","r","r","r"))
```

---

*Room 40 | 2025 Season | Generated via Sleeper API*
